Energy and the CES production function

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Deleted some unused code.

<<Models_CSP>>=
#
# Models that adhere to the cost-share principle
# 
modelsCSP <- list()
# Output elasticities based on cost share principle
alphaCSP <- 0.3 # Fraction of national accounts spent on capital
betaCSP <- 0.7 # Fraction of national accounts spent on labor
for (country in countries){
  for (adj in c("unadjusted", "adjusted")){
    # Replace with better code later. 
    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
    # or something like that.
    form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
    yVar <- as.name(summands(form, n=1, right=FALSE))
    kVar <- as.name(summands(form, n=1))
    lVar <- as.name(summands(form, n=2))
    tVar <- as.name(summands(form, n=3))
    data <- historicalData[[country]]
    formula <- substitute(
      log(Y) - (alpha_1 * log(K) + alpha_2 * log(L)) ~ T,
      list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
    )
    # Cobb-Douglas
    cdModCSP <- 
      eval(substitute( 
        plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
            optimize = FALSE),
        list(formula = formula)))

@@

    # store the result in our list
    modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
    # CES
    # The only CES models that can adhere to the CSP are models where
    # alpha values are constant with respect to time. 
    # I.e., models where energy is not included AND where rho_1 = 0.
    # CES models where rho_1 = 0 are the Cobb-Douglas model.
    # Convienently, we previously fit that model 
    # with the required output elasticities.
    cesModCSP <- cdModCSP

    cesModCSP$coefficients <- 
      c(cesModCSP$coefficients, 
        c(delta_1 = as.vector(cesModCSP$coefficients["alpha_1"]),
          delta = 1,
          rho_1 = 0,
          rho = NA)
      )
    cesModCSP$handcrafted <- TRUE
    class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
    # # Again, we need a customized "naturalCoeffs" attribute so that 
    # # the "naturalCoef" function will do the right thing.
    # # "naturalCoeffs" can be based on the same "naturalCoeffs"
    # # from the Cobb-Douglas model, but a few additions are needed.
    # attr(cesModCSP, "naturalCoeffs") <- 
    #   naturalCoef(cdModCSP) %>%
    #   mutate(
    #     delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
    #     delta = 1,
    #     rho_1 = 0, 
    #     rho = NA,
    #     sigma_1 = 1,
    #     sigma_12 = 1,
    #     sigma = NA,
    #     sigma_12_3 = NA
    #   )
    # # Add output elasticities (as a function of time) to this model.
    # # This would have been done by a "fortify" function, 
    # # but this is not a typical CES model, so we can't "fortify" it.
    # # Add other metadata, too.
    # cesModCSP$data <- cesModCSP$data %>%
    #   mutate(
    #     oe1 = alphaCSP,
    #     oe2 = betaCSP,
    #     oe3 = 0,
    #     Country = country, 
    #     flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
    #     energy  = "Without energy",
    #     model   = "CES", 
    #     nest    = "kl",
    #     CSP     = "w/ CSP"
    #   )
    modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
  }
}

>>>>

<<Models_CSP>>=
#
# Models that adhere to the cost-share principle
# 
modelsCSP <- list()
# Output elasticities based on cost share principle
alphaCSP <- 0.3 # Fraction of national accounts spent on capital
betaCSP <- 0.7 # Fraction of national accounts spent on labor
for (country in countries){
  for (adj in c("unadjusted", "adjusted")){

    # Cobb-Douglas

    # Pull variables out of the formulas for use in fitting the model.
    form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
    yVar <- as.name(summands(form, n=1, right=FALSE))
    kVar <- as.name(summands(form, n=1))
    lVar <- as.name(summands(form, n=2))
    tVar <- as.name(summands(form, n=3))
    data <- historicalData[[country]]
    formula <- substitute(
      log(Y) - (alpha_1 * log(K) + alpha_2 * log(L)) ~ T,
      list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
    )
    # Cobb-Douglas
    cdModCSP <- 
      eval(substitute( 
        plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
            optimize = FALSE),
        list(formula = formula)))

@@

    # store the result in our list
    modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP

    # CES

    # The only CES models that can adhere to the CSP are models where
    # alpha values are constant with respect to time. 
    # I.e., models where energy is not included AND where rho_1 = 0.
    # CES models where rho_1 = 0 are the Cobb-Douglas model.
    # Convienently, we previously fit that model 
    # with the required output elasticities.
    cesModCSP <- cdModCSP

    cesModCSP$coefficients <- 
      c(cesModCSP$coefficients, 
        c(delta_1 = as.vector(cesModCSP$coefficients["alpha_1"]),
          delta = 1,
          rho_1 = 0,
          rho = NA)
      )
    cesModCSP$handcrafted <- TRUE
    class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
    modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
  }
}
